An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
start topk app

In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix... remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$\raft{Jessie, you consistently forget the $p$ (was $u \in \prop{L'}$)}.
From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
\begin{align}\label{eq:ell-2}
\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}|~.
\end{align}
We now see that $\ell'$ is essentially $\elltopk$ (extended to smaller sets) plus an additional cardinality term.

@@

\begin{lemma}\label{lem:top-k-polyhedral}
$L'$ is a polyhedral loss.
\end{lemma}
\begin{proof}
Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
\end{proof}
By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.

\begin{lemma}\label{lem:top-k-optimal-corners}
	For all $p \in \simplex$, there is a $u \in \{ u \in \{0,1\}^n : \|u\|_1 \leq k\}$ such that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L'(u)}$.
\end{lemma}
\begin{proof}[Sketch]
  First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.

>>>>

In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix... remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
From Lemma~\ref{lem:loss-restrict}\raft{was Lemma~\ref{lem:top-k-surrogate-embeds}}, then, $L'$ must embed $L'|_\U$, which gives us $\ell':\R'\to\reals^\Y_+$ via the natural embedding from sets $\R' = \{r \subseteq [n] : |r| \leq k\}$ to their indicator vectors.
\begin{align}\label{eq:ell-2}
\ell'(r)_y &= \Ind{y \not\in r} + \tfrac 1 k |r \setminus \{y\}|~.
\end{align}
We now see that $\ell'$ is essentially $\elltopk$ (extended to smaller sets) plus an additional cardinality term.

@@

\begin{lemma}\label{lem:top-k-polyhedral}
$L'$ is a polyhedral loss.
\end{lemma}
\begin{proof}
Observe $L'$ can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \ones - e_y$, and the max comes from selecting the $u_i$ elements with highest weight.
\end{proof}
%By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L'}$ is also polyhedral.

Let $\U = \{u \in \{0,1\}^n : |u\|_0 \leq k\}$.
We next see that $\U$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
\end{lemma}
\begin{proof}
  First, observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
